Abstractions for Type-Level Programming

### 2022-04-07 preprint.tex
Add Richard's comments

@@

\noindent
We could have equivalently defined |getName| by omitting the |dependent| qualifier and writing its result type explicitly.
The difference between the two would only be matter of syntax.

Scala requires recursive methods to have an explicit result type, and this restriction also applies to |dependent| methods.
However, in the case of a |dependent| method, an explicit result type is only used as an upper bound for the actual precise result type and will only be used to type-check the method's body.
At other call sites, the (precise) inferred result type is used.
Bounds of dependent methods are written using a special syntax (|<: T|).

@@

Scala's type system permits uncontrolled side effects in programs.
Given the absence of an effect system, result types of methods do not convey any information about the potential use of side effects in the method body.
The situation is analogous for |dependent| methods.
Since we uniformly approximate all side effects, we avoid the situation where a type refers to a value that may be modified during the program execution.
For instance, if |z| is a mutable integer variable, we will never introduce |z| in a singleton type.
However, we can still assign singleton types to expressions containing |z|, for example, we can type |Cons(z, Nil())| as |{ Cons(_: Int, Nil()) }|.

@@

>>>>

% TODO: Add a sentence about the state of adoptions of these ideas

@@

\noindent
We could have equivalently defined |getName| by omitting the |dependent| qualifier and writing its result type explicitly.
The difference between the two would only be matter of syntax.
% TODO: say something about the fact that generalized singleton types are not singletons...

Scala requires recursive methods to have an explicit result type, and this restriction also applies to |dependent| methods.
However, in the case of a |dependent| method, an explicit result type only serves as an upper bound used to type-check the method's body.
At other call sites, the (precise) inferred result type is used.
Bounds of dependent methods are written using a special syntax (|<: T|).

@@

Scala's type system permits uncontrolled side effects in programs.
Given the absence of an effect system, result types of methods do not convey any information about the potential use of side effects in the method body.
The situation is analogous for |dependent| methods.
Since we uniformly approximate all side effects, we avoid the situation where a type refers to a value that may be modified during the program execution.
For instance, if |z| is a mutable integer variable, we will never introduce |z| in a singleton type.
However, we can still assign singleton types to expressions containing |z|, for example, we can type |Cons(z, Nil())| as |{ Cons(_: Int, Nil()) }|.
% TODO: More generally, when dependently typed functions call into a non-dependently typed one, ...

@@

% TODO: Add an example
